Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
new values

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$             & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 584.33  &  516.42  & 679.67 & 613.98   \\ \midrule
Median & 49.38    & 53.00  & 69.25              & 56.93               \\ \midrule
Variance & 1223.08  &  1148.11  & 1352.37  & 1294.87   \\ \midrule
Shapiro &\makecell{W = 0.53 \\ p = 7.13 x $10^{-26}$} & \makecell{W = 0.49 \\ p = 1.22 x $10^{-26}$} & \makecell{W = 0.55 \\ p = 2.64 x $10^{-25}$} & \makecell{W = 0.52 \\ p = 5.07 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 69.51 \\ p-value = 5.44 x $10^{-15}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}

>>>>

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$             & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 584.33 (580.03)  &  516.42 (502.60) & 679.67 (566.99) & 613.98 (491.47)  \\ \midrule
Median & 49.38 (47.5)   & 53.00 (54.5)  & 69.25 (42.72)             & 56.93 (40)\\ \midrule
Variance & 1223.08 (1236.94)  &  1148.11 (1149.09)  & 1352.37 (1229.4) & 1294.87  (1143.02) \\ \midrule
Shapiro &\makecell{W = 0.53 \\ p = 7.13 x $10^{-26}$} & \makecell{W = 0.49 \\ p = 1.22 x $10^{-26}$} & \makecell{W = 0.55 \\ p = 2.64 x $10^{-25}$} & \makecell{W = 0.52 \\ p = 5.07 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 69.51 \\ p-value = 5.44 x $10^{-15}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}
